---
title: "Data Product assignment"
author: "Ploulack"
date: "27/06/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE)
```


```{r message=FALSE}
library(tidyverse)
library(leaflet)
library(tidyr)
library(purrr)
```

## Introduction to the Ash borer problem
in the 90s the ash borer was introduced in north america accidentally, probably through shipping containers.
The invasion was detected in michigan in 2002.
in the absence of parasite wasps, the insect's larvae kills all trees in an area.
In urban environment where trees provide hold much higher value that in forest, pesticide injection in the tree is the only available answer.
We provide map of Montreal's ash trees injected. Click on tree to get year of injection.

## Getting the data

Montreal public data repository hosts the file.

```{r, message=FALSE, results='hide', warning=FALSE, cache=TRUE}
p2016 <- "http://donnees.ville.montreal.qc.ca/dataset/ebb813dd-a93f-4fb0-8137-80492a30a1fa/resource/0a5984e4-752f-401e-b2d9-aa0567535d39/download/frenepublicinjection2016.csv"
p2015 <- "http://donnees.ville.montreal.qc.ca/dataset/ebb813dd-a93f-4fb0-8137-80492a30a1fa/resource/a57f787f-bde9-4a59-88d1-4ae742edd9b8/download/frenepublicinjection2015.csv"
p2014 <- "http://donnees.ville.montreal.qc.ca/dataset/ebb813dd-a93f-4fb0-8137-80492a30a1fa/resource/27a5c89f-6bd5-44ac-bbe9-8a0fdc9858f8/download/frenepublicinjection2014.csv"

ash <- map_df(c(p2014,p2015,p2016), read_csv)
```


## Interactive map
Zoom in to clear the clusters and click on any 'tree' to get the latest year of injection for pesticide treatment.

```{r, fig.align='center',fig.asp= 2, out.width="100%",fig.cap= "Ash trees in Montreal treated against the ash borer"}
ash %>%
        select(latitude, longitude, Injections) %>%
        mutate(Injections = as.character(Injections)) %>%
        leaflet() %>%
        addTiles() %>%
        addMarkers(clusterOptions = markerClusterOptions(), popup = ~Injections ) %>%
        setView(lat = 45.53889, lng = -73.67858 ,zoom = 12)
```


And this conludes our montreal report on the battle against the ash borer.
