---
title: "Ash trees treatment in Montreal"
author: "Ploulack"
date: "29/06/2017"
output: ioslides_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE)
```


```{r message=FALSE, echo=FALSE}
library(tidyverse)
library(leaflet)
library(tidyr)
library(purrr)
library(plotly)
```

## Introduction to the Ash borer problem
- in the 90s the ash borer was introduced in north america accidentally, probably through shipping containers.
- The invasion was detected in michigan in 2002.
- In the absence of parasite wasps, the insect's larvae kills all trees in an area.
- In urban environment where trees provide hold much higher value that in forest, pesticide injection in the tree is the only available answer.

## Getting the data

Montreal public data repository hosts the file.

```{r, message=FALSE, results='hide', warning=FALSE, cache=FALSE, echo=FALSE}
p2016 <- "http://donnees.ville.montreal.qc.ca/dataset/ebb813dd-a93f-4fb0-8137-80492a30a1fa/resource/0a5984e4-752f-401e-b2d9-aa0567535d39/download/frenepublicinjection2016.csv"
p2015 <- "http://donnees.ville.montreal.qc.ca/dataset/ebb813dd-a93f-4fb0-8137-80492a30a1fa/resource/a57f787f-bde9-4a59-88d1-4ae742edd9b8/download/frenepublicinjection2015.csv"
p2014 <- "http://donnees.ville.montreal.qc.ca/dataset/ebb813dd-a93f-4fb0-8137-80492a30a1fa/resource/27a5c89f-6bd5-44ac-bbe9-8a0fdc9858f8/download/frenepublicinjection2014.csv"

ash <- map_df(c(p2014,p2015,p2016), read_csv) %>%
        mutate( Year = as.factor(Injections), District = Nom_arrond)
```

## Interactive plotly: code
Plotly offers a quick way to interactively feel where are ash treated the most in Montreal.
We use plotly's ability to convert from ggplot which we're familiar with.

```{r, cache=TRUE}
g <- ggplot(ash) +
        aes(x = Year, fill = District) +
        geom_bar(stat = "count") +
        labs(title = "Ash trees treated against borer per year",
             y = "Nb of Trees",
             x = "")
```

## Plotly with command ggplotly(g)
```{r, warning=FALSE, echo=FALSE, message=FALSE, fig.height= 6, fig.width= 10}
ggplotly(g)
```